Large and Infinitary Quotient Inductive-Inductive Types

### 2020-04-12 draft/paper.tex
acks

%% Acknowledgments
\begin{acks}
This work was supported by the European Union, co-financed by the
European Social Fund (EFOP-3.6.3-VEKOP-16-2017-00002) and COST Action
EUTypes CA15123.
\end{acks}

>>>>

%% Acknowledgments
\begin{acks}
The first author was supported by the European Union, co-financed by the
European Social Fund (EFOP-3.6.3-VEKOP-16-2017-00002). The second author was
supported by the National Research, Development and Innovation Fund of Hungary,
financed under the Thematic Excellence Programme funding scheme, Project
no. ED18-1-2019-0030 (Application-specific highly reliable IT solutions), by the
New National Excellence Program of the Ministry for Innovation and Technology,
Project no. \'UNKP-19-4-ELTE-874, and by the Bolyai Fellowship of the Hungarian
Academy of Sciences, Project no. BO/00659/19/3.
\end{acks}
